---
title: "Week2-summarystats"
output:
  html_document: default
  pdf_document: default
date: "2025-10-11"
---
# Question 1 
1. Compute the mean, median, and standard deviation of the variable miles per gallon.
Recall that the column of a dataframe can be extracted using $ i.e., mtcars$mpg
```{r}
mpg <- mtcars$mpg
mpg
mean(mpg)
median(mpg)
sd(mpg)

```
Construct a histogram of the horsepower of the vehicles in the dataset. Given the shape
of your histogram, will the mean be greater than, less than or approximately equal to the
median? Estimate the median from your graph, then verify your answer using R.

```{r}
hp <- mtcars$hp

hist(hp)

mean(hp)

```
Mean is less than median as more values are concentrated at left of the histogram

# Question2 
Construct a boxplot and a stem and leaf plot of the horsepower. Compare the properties
of these two graphs with the histogram constructed in the previous question. What is
similar, and what is different?

```{r}
boxplot(hp)
quantile(hp, prob = c( 0.25, 0.5 , 0.75))
IQR_val <- IQR((hp))
1.5*IQR_val

96-1.5*IQR_val

180 + 1.5*IQR_val
